### 2013-07-19 doc/dissertation/document/chapters/nonlinear_problem/nonlinear_problem.tex
adding fanm output for step at re200

%%---------------------------------------------------------------------------%%
\section{Navier-Stokes Benchmark Problems\ }
\label{sec:ns_benchmarks}
To verify the FANM method for nonlinear problems, we choose benchmark
solutions for the 2-dimensional, steady, incompressible Navier-Stokes
equations on a rectilinear grid in much the same way as Shadid and
Pawlowski's work on Newton-Krylov methods for the solution of these
equations \citep{shadid_inexact_1997,pawlowski_globalization_2006}. We
define these equations as follows:
\begin{subequations}
  \begin{gather}
    \rho \ve{u} \cdot \nabla \ve{u} - \nabla \cdot \ve{T} - \rho
    \ve{g} = \ve{0}
    \label{eq:ns_momentum}\\
    \nabla \cdot \ve{u} = 0
    \label{eq:ns_continuity}\\
    \rho C_p \ve{u} \cdot \nabla T + \nabla \cdot \ve{q} = 0\:,
    \label{eq:ns_energy}
  \end{gather}
  \label{eq:navier_stokes}
\end{subequations}
where $\rho$ is the fluid density, $\ve{u}$ is the fluid velocity,
$C_p$ the specific heat capacity at constant pressure of the fluid,
$T$ the temperature of the fluid, and $\ve{g}$ the acceleration due to
gravity. Eq~(\ref{eq:ns_momentum}) provides momentum transport,
Eq~(\ref{eq:ns_continuity}) provides the mass balance, and
Eq~(\ref{eq:ns_energy}) provides energy transport with viscous
dissipation effects neglected. In addition, we close the system with
the following equations:
\begin{subequations}
  \begin{gather}
    \ve{T} = -P \ve{I} + \mu[\nabla \ve{u} + \nabla \ve{u}^T]
    \label{eq:ns_stress_tensor}\\
    \ve{q} = - k \nabla T\:,
    \label{eq:ns_heat_flux}
  \end{gather}
  \label{eq:ns_closure}
\end{subequations}
where $\ve{T}$ is the stress tensor, $P$ is the hydrodynamic pressure,
$\mu$ is the dynamic viscosity of the fluid, $\ve{q}$ is the heat flux
in the fluid, and $k$ is the thermal conductivity of the fluid. This
set of strongly coupled equations possesses both the nonlinearities
and asymmetries that we are seeking for qualification of the FANM
method. Further, physical parameters within these equations can be
tuned to enhance the nonlinearities. We will then apply these
equations to the following two standard benchmark problems that cover
convection dominated flow and flow dominated by intertial forces.

@@

@@

A Drekar model of thermal convection cavity problem was solved using
both the Newton-Krylov solver and a FANM solver for Reynolds numbers
of 100, 300, 500, and 700 on a $50 \times 50$ square
grid. Table~\ref{tab:thermal_convection_parameters} gives the physical
parameters of the problem and
Table~\ref{tab:convection_mcsa_parameters} gives the MCSA solver
parameters used within the FANM method. Variation in the Reynolds
number of the system was achieved by keeping the parameters given in
Table~\ref{tab:thermal_convection_parameters} fixed and varying the
fluid velocity in the $x$ direction on the top boundary. In addition
to multigrid preconditioning for the linear solution at each Newton
step, a polynomial line search method was used as a means of
globalization assisting the Newton correction computation as outlined
by Pawlowski in \citep{pawlowski_globalization_2006} while the forcing
term was again computed using method 2 from Shadid's work
\citep{shadid_inexact_1997}.

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lcc}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{c}{Value}&
      \multicolumn{1}{c}{Units}\\\hline
      $x_{min}$ & 0.0 & $m$ \\
      $x_{max}$ & 1.0 & $m$ \\
      $y_{min}$ & 0.0 & $m$ \\
      $y_{max}$ & 1.0 & $m$ \\
      $N_x$ & 50 & - \\
      $N_y$ & 50 & - \\
      $DOFs$ & 7803 & - \\
      Density & 1.0 & $kg / m^3$ \\
      Dynamic Viscosity & 0.71 & $(N \times s) / m^2$ \\
      Kinematic Viscosity & 0.71 & $m^2 / s$ \\
      Gravitational Acceleration & 10 & $m / s^2$ \\
      Cavity Characteristic Length & 1.0 & $m$ \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Lid driven cavity FANM verification model
      problem parameters.}  \textit{The Navier-Stokes equations in 2
      dimensions are used for the model problem. The Reynolds number
      is varied by modifying the velocity magnitude on the upper
      boundary to induce flow driven by inertial forces.}}
  \label{tab:lid_driven_parameters}
\end{table}

@@

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lcc}\hline\hline
      \multicolumn{1}{l}{Rayleigh Number}& 
      \multicolumn{1}{c}{Newton-Krylov Speedup}\\
      \hline
      \sn{1}{3} & 338 \\
      \sn{1}{4} & 336 \\
      \sn{1}{5} & 346 \\
      \sn{1}{6} & 465 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Thermal convection cavity Newton-Krylov speedup
      over FANM method.} \textit{Speedup values are rounded to the
      nearest integer. The results presented here were obtained from
      the benchmark verification calculations.}}
  \label{tab:convection_speedup_comparison}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lcc}\hline\hline
      \multicolumn{1}{l}{Reynolds Number}& 
      \multicolumn{1}{c}{Newton-Krylov Speedup}\\
      \hline
      100 & 299 \\
      300 & 322 \\
      500 & 288 \\
      700 & 488 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Lid driven cavity Newton-Krylov speedup
      over FANM method.} \textit{Speedup values are rounded to the
      nearest integer. The results presented here were obtained from
      the benchmark verification calculations.}}
  \label{tab:driven_speedup_comparison}
\end{table}

>>>>

%%---------------------------------------------------------------------------%%
\section{Navier-Stokes Benchmark Problems\ }
\label{sec:ns_benchmarks}
To verify the FANM method for nonlinear problems, we choose benchmark
solutions for the 2-dimensional, steady, incompressible Navier-Stokes
equations on a rectilinear grid in much the same way as Shadid and
Pawlowski's work on Newton-Krylov methods for the solution of these
equations \citep{shadid_inexact_1997,pawlowski_globalization_2006}. We
define these equations as follows:
\begin{subequations}
  \begin{gather}
    \rho \ve{u} \cdot \nabla \ve{u} - \nabla \cdot \ve{T} - \rho
    \ve{g} = \ve{0}
    \label{eq:ns_momentum}\\
    \nabla \cdot \ve{u} = 0
    \label{eq:ns_continuity}\\
    \rho C_p \ve{u} \cdot \nabla T + \nabla \cdot \ve{q} = 0\:,
    \label{eq:ns_energy}
  \end{gather}
  \label{eq:navier_stokes}
\end{subequations}
where $\rho$ is the fluid density, $\ve{u}$ is the fluid velocity,
$C_p$ the specific heat capacity at constant pressure of the fluid,
$T$ the temperature of the fluid, and $\ve{g}$ the acceleration due to
gravity. Eq~(\ref{eq:ns_momentum}) provides momentum transport,
Eq~(\ref{eq:ns_continuity}) provides the mass balance, and
Eq~(\ref{eq:ns_energy}) provides energy transport with viscous
dissipation effects neglected. In addition, we close the system with
the following equations:
\begin{subequations}
  \begin{gather}
    \ve{T} = -P \ve{I} + \mu[\nabla \ve{u} + \nabla \ve{u}^T]
    \label{eq:ns_stress_tensor}\\
    \ve{q} = - k \nabla T\:,
    \label{eq:ns_heat_flux}
  \end{gather}
  \label{eq:ns_closure}
\end{subequations}
where $\ve{T}$ is the stress tensor, $P$ is the hydrodynamic pressure,
$\mu$ is the dynamic viscosity of the fluid, $\ve{q}$ is the heat flux
in the fluid, and $k$ is the thermal conductivity of the fluid. This
set of strongly coupled equations possesses both the nonlinearities
and asymmetries that we are seeking for qualification of the FANM
method. Further, physical parameters within these equations can be
tuned to enhance the nonlinearities. We will then apply these
equations to the following three standard benchmark problems that
cover convection dominated flow and flow dominated by intertial
forces in two different geometries.

@@

\subsubsection{Backward-Facing Step Problem}
\label{subsubsec:backward_facing_step}
The third benchmark was generated by Gartling in 1990 and consists of
both flow over a backward step and an outflow boundary condition
\citep{gartling_test_1990}. Using the mass and momentum equations
while neglecting the energy equation, this problem utilizes a longer
domain with a 1/25 aspect ratio used for this work\footnote{The
  literature on this benchmark suggests using a domain with a 1/30
  aspect ratio to reduce the effect of the outflow boundary condition
  on the upstream recirculation zones. Using a 1/25 aspect ratio for
  this work was not observed to disturb the recirculation zones and
  was therefore used to reduce memory pressure on the FANM solver.}
with the boundary conditions as shown in
Figure~\ref{fig:backward_facing_step}.

\begin{figure}[htpb!]
  \begin{center}
    \scalebox{1.2}{
      \input{chapters/nonlinear_problem/backward_facing_step.pdftex_t} }
  \end{center}
  \caption{\textbf{Problem setup for the backward facing step
      benchmark.} \textit{Zero velocity boundary conditions are
      applied at the top and bottom of the domain while the outflow
      boundary condition on the right boundary is represented by zero
      stress tensor components in the direction of the flow. For the
      inlet conditions, the left boundary is split such that the top
      half has a fully formed parabolic flow profile and the bottom
      half has a zero velocity condition, simulating flow over a
      step.}}
  \label{fig:backward_facing_step}
\end{figure}

In this problem, the inflow condition is specified by a fully-formed
parabolic flow profile over a zero velocity boundary representing a
step. The flow over this step will generate a recirculating backflow
under the inlet flow towards the step and at higher Reynolds numbers a
recirculating zone will form farther downstream from the step. As in
the lid driven cavity problem, the nonlinear behavior of this
benchmark and the difficulty in obtaining a solution is dictated by
the Reynolds number of the fluid. In Shadid's work, a Reynolds numbers
up to 800 were used.

Compared to the lid driven cavity benchmark, the flow over a backward
step is much more representative of flow driven by inertial forces in
a nuclear reactor that may encounter several obstacles along the flow
path. For example, spacer grids in fuel assemblies or mixing vanes
designed to induce turbulence and improve heat transfer will create
recirculation zones much like those observed for this benchmark
problem. Figure~\ref{fig:step_velocity_isocurves} gives the velocity
magnitude contours for solutions to this problem with Reynolds numbers
of 200, 400, 600, and 800.

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/nonlinear_problem/driven_velocity_isocurves.png}
  \end{center}
  \caption{\textbf{Velocity magnitude isocurves from solution to the
      thermal convection cavity problem.} \textit{From top to bottom:
      Re = 200, Re = 400, Re = 600, Re = 800. Isocurves on unit
      velocity scale from 0 to 1 with divisions of 0.05 for each
      calculation.}}
  \label{fig:driven_velocity_isocurves}
\end{figure}

@@

A Drekar model of thermal convection cavity problem was solved using
both the Newton-Krylov solver and a FANM solver for Reynolds numbers
of 100, 300, 500, and 700 on a $50 \times 50$ square
grid. Table~\ref{tab:lid_driven_parameters} gives the physical
parameters of the problem and
Table~\ref{tab:driven_mcsa_parameters} gives the MCSA solver
parameters used within the FANM method. Variation in the Reynolds
number of the system was achieved by keeping the parameters given in
Table~\ref{tab:lid_driven_parameters} fixed and varying the
fluid velocity in the $x$ direction on the top boundary. In addition
to multigrid preconditioning for the linear solution at each Newton
step, a polynomial line search method was used as a means of
globalization assisting the Newton correction computation as outlined
by Pawlowski in \citep{pawlowski_globalization_2006} while the forcing
term was again computed using method 2 from Shadid's work
\citep{shadid_inexact_1997}.

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lcc}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{c}{Value}&
      \multicolumn{1}{c}{Units}\\\hline
      $x_{min}$ & 0.0 & $m$ \\
      $x_{max}$ & 1.0 & $m$ \\
      $y_{min}$ & 0.0 & $m$ \\
      $y_{max}$ & 1.0 & $m$ \\
      $N_x$ & 50 & - \\
      $N_y$ & 50 & - \\
      $DOFs$ & 7803 & - \\
      Density & 1.0 & $kg / m^3$ \\
      Dynamic Viscosity & 0.71 & $(N \times s) / m^2$ \\
      Kinematic Viscosity & 0.71 & $m^2 / s$ \\
      Cavity Characteristic Length & 1.0 & $m$ \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Lid driven cavity FANM verification model
      problem parameters.}  \textit{The Navier-Stokes equations in 2
      dimensions are used for the model problem. The Reynolds number
      is varied by modifying the velocity magnitude on the upper
      boundary to induce flow driven by inertial forces.}}
  \label{tab:lid_driven_parameters}
\end{table}

@@

\subsection{Backward Facing Step Results}
\label{subsec:backward_step_verification}

A Drekar model of the backward facing step problem was solved using
both the Newton-Krylov solver and a FANM solver for Reynolds numbers
of 200, 400, 600, and 800 on a $20 \times 250$ rectangular
grid. Table~\ref{tab:backward_step_parameters} gives the physical
parameters of the problem and Table~\ref{tab:step_mcsa_parameters}
gives the MCSA solver parameters used within the FANM
method. Variation in the Reynolds number of the system was achieved by
keeping the parameters given in
Table~\ref{tab:backward_step_parameters} fixed and varying the maximum
fluid velocity in the parabolic inlet condition. In addition to
multigrid preconditioning for the linear solution at each Newton step,
a polynomial line search method was used as a means of globalization
assisting the Newton correction computation as outlined by Pawlowski
in \citep{pawlowski_globalization_2006} while the forcing term was
again computed using method 2 from Shadid's work
\citep{shadid_inexact_1997}.

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lcc}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{c}{Value}&
      \multicolumn{1}{c}{Units}\\\hline
      $x_{min}$ & 0.0 & $m$ \\
      $x_{max}$ & 1.0 & $m$ \\
      $y_{min}$ & 0.0 & $m$ \\
      $y_{max}$ & 1.0 & $m$ \\
      $N_x$ & 50 & - \\
      $N_y$ & 50 & - \\
      $DOFs$ & 7803 & - \\
      Density & 1.0 & $kg / m^3$ \\
      Dynamic Viscosity & 0.71 & $(N \times s) / m^2$ \\
      Kinematic Viscosity & 0.71 & $m^2 / s$ \\
      Channel Width & 1.0 & $m$ \\
      Step Height & 0.5 & $m$ \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Backward facing step FANM verification model
      problem parameters.}  \textit{The Navier-Stokes equations in 2
      dimensions are used for the model problem. The Reynolds number
      is varied by modifying the velocity magnitude on the upper
      boundary to induce flow step by inertial forces.}}
  \label{tab:backward_step_parameters}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lc}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{c}{Value}\\\hline
      Weight Cutoff & \sn{1}{-2} \\
      Fixed Point Iteration & Richardson \\
      Estimator & Adjoint Collision \\
      Histories, Re=200 & 600,000 per iteration \\
      Histories, Re=400 & 600,000 per iteration \\
      Histories, Re=600 & 600,000 per iteration \\
      Histories, Re=800 & 1,000,000 per iteration \\
      Reduced Domain Fill Level, Re=200 & 200 \\
      Reduced Domain Fill Level, Re=400 & 200 \\
      Reduced Domain Fill Level, Re=600 & 200 \\
      Reduced Domain Fill Level, Re=800 & 300 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Backward facing step FANM verification MCSA solver
      parameters.} \textit{No relaxation parameters or variance
      reduction techniques were used with MCSA other than the reduced
      domain approximation. Different values of fill level for the
      reduced domain approximation and histories per iteration were
      used at different Reynolds numbers due to convergence
      requirements.}}
  \label{tab:step_mcsa_parameters}
\end{table}

For the verification calculations, at each Reynolds number variation
the global minimum, maximum, and average values were recorded for the
fluid velocity in the x and y directions and the fluid
pressure. Tables~\ref{tab:step_re200_results},
\ref{tab:step_re400_results}, \ref{tab:step_re600_results}, and
\ref{tab:step_re800_results} give the results of these
computations. As with the thermal convection problem, the negative
pressures computed are due to a relative pressure being reported. For
each of the data points given, both Newton-Krylov solutions and FANM
solutions computed identical numerical results for all of these global
values. The norm of the converged nonlinear residual for the
calculations is given in
Table~\ref{tab:step_residual_norm_comparison}. All computed global
values were within these tolerances.

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U_x$ & \\
      Minimum $U_x$ & \\ 
      Maximum $U_x$ & \\
      \hline
      Average $U_y$ & \\
      Minimum $U_y$ & \\ 
      Maximum $U_y$ & \\ 
      \hline
      Average $P$ & \\ 
      Minimum $P$ & \\ 
      Maximum $P$ & \\ 
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Backward facing step cavity FANM verification for a
      Reynolds number of 200.} \textit{The values reported are global
      minima, maxima, and averages for each variable in the
      problem. The velocity is given in components in the $x$ and $y$
      directions.}}
  \label{tab:step_re200_results}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U_x$ & \\
      Minimum $U_x$ & \\
      Maximum $U_x$ & \\
      \hline
      Average $U_y$ & \\
      Minimum $U_y$ & \\
      Maximum $U_y$ & \\
      \hline
      Average $P$ & \\
      Minimum $P$ & \\
      Maximum $P$ & \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Backward facing step cavity FANM verification for a
      Reynolds number of 400.} \textit{The values reported are global
      minima, maxima, and averages for each variable in the
      problem. The velocity is given in components in the $x$ and $y$
      directions.}}
  \label{tab:step_re400_results}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U_x$ & \\
      Minimum $U_x$ & \\
      Maximum $U_x$ & \\
      \hline
      Average $U_y$ & \\
      Minimum $U_y$ & \\
      Maximum $U_y$ & \\
      \hline
      Average $P$ & \\
      Minimum $P$ & \\
      Maximum $P$ & \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Backward facing step cavity FANM verification for a
      Reynolds number of 600.} \textit{The values reported are global
      minima, maxima, and averages for each variable in the
      problem. The velocity is given in components in the $x$ and $y$
      directions.}}
  \label{tab:step_re600_results}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lll}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{l}{Newton-Krylov Result}&
      \multicolumn{1}{l}{FANM Result}\\
      \hline
      Average $U_x$ & \\
      Minimum $U_x$ & \\
      Maximum $U_x$ & \\
      \hline
      Average $U_y$ & \\
      Minimum $U_y$ & \\
      Maximum $U_y$ & \\
      \hline
      Average $P$ & \\
      Minimum $P$ & \\
      Maximum $P$ & \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Backward facing step cavity FANM verification for a
      Reynolds number of 800.} \textit{The values reported are global
      minima, maxima, and averages for each variable in the
      problem. The velocity is given in components in the $x$ and $y$
      directions.}}
  \label{tab:step_re800_results}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lcc}\hline\hline
      \multicolumn{1}{l}{Reynolds Number}& 
      \multicolumn{1}{c}{Newton Krylov $||\ve{F(\ve{u})}||$}&
      \multicolumn{1}{c}{FANM $||\ve{F(\ve{u})}||$}\\
      \hline
      200 & \\
      400 & \\
      600 & \\
      800 & \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Backward facing step cavity nonlinear residual norm
      achieved convergence.} \textit{The results presented here were
      obtained from the benchmark verification calculations.}}
  \label{tab:step_residual_norm_comparison}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lc}\hline\hline
      \multicolumn{1}{l}{Rayleigh Number}& 
      \multicolumn{1}{c}{Newton-Krylov Speedup}\\
      \hline
      \sn{1}{3} & 338 \\
      \sn{1}{4} & 336 \\
      \sn{1}{5} & 346 \\
      \sn{1}{6} & 465 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Thermal convection cavity Newton-Krylov speedup
      over FANM method.} \textit{Speedup values are rounded to the
      nearest integer. The results presented here were obtained from
      the benchmark verification calculations.}}
  \label{tab:convection_speedup_comparison}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lc}\hline\hline
      \multicolumn{1}{l}{Reynolds Number}& 
      \multicolumn{1}{c}{Newton-Krylov Speedup}\\
      \hline
      100 & 299 \\
      300 & 322 \\
      500 & 288 \\
      700 & 488 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Lid driven cavity Newton-Krylov speedup over FANM
      method.} \textit{Speedup values are rounded to the nearest
      integer. The results presented here were obtained from the
      benchmark verification calculations.}}
  \label{tab:driven_speedup_comparison}
\end{table}

\subsection{Backward Facing Step Results}
\label{subsec:backward_step_comparison}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lcc}\hline\hline
      \multicolumn{1}{l}{Reynolds Number}& 
      \multicolumn{1}{c}{Newton-Krylov Iterations}&
      \multicolumn{1}{c}{FANM Iterations}\\
      \hline
      200 & \\
      400 & \\
      600 & \\
      800 & \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Backward facing step cavity nonlinear iteration
      results for the performance comparison.} \textit{The results
      presented here were obtained from the benchmark verification
      calculations.}}
  \label{tab:step_nonlinear_iter_comparison}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lcc}\hline\hline
      \multicolumn{1}{l}{Reynolds Number}& 
      \multicolumn{1}{c}{GMRES Iterations}&
      \multicolumn{1}{c}{MCSA Iterations}\\
      \hline
      200 & \\
      400 & \\
      600 & \\
      800 & \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Backward facing step cavity total sum of linear
      iterations for all nonlinear iterations.} \textit{The results
      presented here were obtained from the benchmark verification
      calculations.}}
  \label{tab:step_linear_iter_comparison}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lc}\hline\hline
      \multicolumn{1}{l}{Reynolds Number}& 
      \multicolumn{1}{c}{Newton-Krylov Speedup}\\
      \hline
      200 & \\
      400 & \\
      600 & \\
      800 & \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Backward facing step cavity Newton-Krylov speedup
      over FANM method.} \textit{Speedup values are rounded to the
      nearest integer. The results presented here were obtained from
      the benchmark verification calculations.}}
  \label{tab:step_speedup_comparison}
\end{table}
